\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[sfdefault,light]{roboto} 
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}

\usepackage[sfdefault,light]{roboto} 
\usepackage[sfdefault,light]{roboto} 

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\centering
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}



\begin{center}
    {\bf\LARGE Adarsh Medikonda} \\ \vspace{2pt}
    {(832)-758-0413} \\
    {1310 Chelshurst Way, Spring, TX 77379} \\\vspace{3pt}
    {medikonda.adarsh@gmail.com}\\
    {adarshmedikonda.github.io}\\
\end{center}


%-----------EDUCATION-----------
%\vspace{-2pt}
\section{\bf Education}
\vspace{4pt}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Klein Oak High School}{2015 -- 2019}
      {International Baccalaureate Diploma}{Klein, TX}
      \resumeItemListStart
        \resumeItem{4-year specialization in Computer Science}
      \resumeItemListEnd
      \resumeSubheading
      {Texas A\&M University}{2019 -- ONGOING}
      {Bachelor's Degree in Electronic Systems Engineering Technology}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Related Coursework: ESET 210, ESET 219, ESET 269, CSCE 222, MATH 152, MATH 251.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\vspace{2pt}
\section{\bf Experience}
\vspace{4pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Community, Activity, and Service Volunteering}{2017 -- 2019}
      {}{}
      \vspace{-6pt}
      \resumeItemListStart
        \resumeItem{Over 150 hours volunteering in my community, randing from assisting during Walk MS: Houston to introducing elementary aged children to coding through curated activities}
      \resumeItemListEnd
    \vspace{2pt}
    \resumeSubheading
      {Python Tutoring}{2019 -- 2020}
      {}{}
      \vspace{-6pt}
      \resumeItemListStart
        \resumeItem{Taught Python to a student attending University of Massachusetts Amherst, focusing on problem-solving logic and algorithms.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\vspace{2pt}
\section{\bf Skills}
\vspace{10pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, C++, Java, HTML, CSS, JavaScript.} \\
     \textbf{Operating Systems}{: Windows, Linux (Debian, Manjaro, Arch).} \\
     \textbf{Frontend Development}{: ReactJS, ElectronJS.}\\
     \textbf{Machine Learning} {: TensorFlow 2.} \\
     \textbf{Cloud}{: Heroku.} \\
     \textbf{Word Processors}{: \LaTeX, Microsoft Office} \\
     \textbf{Embedded Engineering}{: Arduino, Raspberry Pi, Texas Instruments MSP432.} \\
    }}
 \end{itemize}
 \vspace{-10pt}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Programming Experience}{}
      {}{}
      \vspace{-10pt}
      \resumeItemListStart
        \resumeItem{4 years of experience writing Java programs.}
        \resumeItem{2 years of experience with Python.}
        \resumeItem{1 year of experience with C/C++.}
        \resumeItem{Extensive practice with OOP Design using both Java and C++.}
        \resumeItem{Competed in multiple team-based coding competetitions.}
        \resumeItem{Heavy interest in algorithmic design and combinatorics.}
        \resumeItem{Implemented functions using Python to efficiently scrape and analyze large scale data from the web.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\vspace{2pt}
\section{\bf Certifications}
\vspace{4pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Certificate in Cyber Security | Universidad Carlos III de Madrid}{2018 -- 2018}
      {Specialization in Network Analysis and Computer Forensics}{Madrid, Spain}
      \resumeItemListStart
        \resumeItem{Real-world application of reverse engineering, vulnerability management, and pentesting}
        \resumeItem{Experience with Metasploit}
    \resumeItemListEnd
    \resumeSubheading
      {Fundamentals of Deep Learning for Computer Vision Certification | NVIDIA}{2019 -- 2019}
      {Neural Network Imaging and Deployment}{College Station, TX}
      \resumeItemListStart
        \resumeItem{Trained and deployed deep learning models}
        \resumeItem{Practiced data augmentation to more accurately create models}
        \resumeItem{Experience with Python3, TensorFlow 2 with Keras, and Pandas}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}